Improved Bounds for Online Balanced Repartitioning

### 2020-04-02 paper/paper.tex
On cascade

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
    \rowcolor{gray!50}
    \textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
      \textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 3\hspace{0.3cm}(\S 9.3) \\ 
      \rowcolor{gray!25}
      \textbf{$k=3$}&  $1357\cdot \ell - 245 = \Omega(\ell)$\hspace{0.3cm}(\S 9.3)& $O(\ell)$\hspace{0.3cm}(\S 9.3)\\
      \textbf{$\ell=2$}&  $2k-1$\hspace{0.3cm}(\S 9.3)&\hspace{0.3cm}$O(k^2)$\hspace{0.3cm}\cite{repartition-disc}\\
      \rowcolor{gray!25}
      $\ell \geq 3$& $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S 9.3)&$O(k^2 \cdot \ell^2)$\hspace{0.3cm}\cite{repartition-disc} \\
      Perfect partition & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S 9.3)&$O(k \cdot \ell)$\hspace{0.3cm} (\S 9) \\
    \end{tabular}
                \caption{Overview of the results. Most specific cases are tight. The general case still has a significant gap between the lower bound and the upper bound. If either $k$ or $\ell$ is missing from a variant description, it is assumed to be arbitrary.
                  }
  \label{tab:overview}
  \vspace{-7mm}
\end{table*}

@@

\maciek{Figure: cluster types}

@@

In our analysis, we distinguish among three types of clusters: $C_1, C_2, C_3$. In a cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.
Before bounding the competitive ratio of \TAlg, we introduce the lemma that estimates the cost of a single repartition of \TAlg.

@@

>>>>

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
    \rowcolor{gray!50}
    \textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
      \textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 3\hspace{0.3cm}(\S 9.3) \\ 
      \rowcolor{gray!25}
      \textbf{$k=3$}&  $27\cdot \ell $\hspace{0.3cm}(\S 9.3)& $O(\ell)$\hspace{0.3cm}(\S 9.3)\\
      \textbf{$\ell=2$}&  $2k-1$\hspace{0.3cm}(\S 9.3)&\hspace{0.3cm}$O(k^2)$\hspace{0.3cm}\cite{repartition-disc}\\
      \rowcolor{gray!25}
      $\ell \geq 3$& $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S 9.3)&$O(k^2 \cdot \ell^2)$\hspace{0.3cm}\cite{repartition-disc} \\
      Perfect partition & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S 9.3)&$O(k \cdot \ell)$\hspace{0.3cm} (\S 9) \\
    \end{tabular}
                \caption{Overview of the results. Most specific cases are tight. The general case still has a significant gap between the lower bound and the upper bound. If either $k$ or $\ell$ is missing from a variant description, it is assumed to be arbitrary.
                  }
  \label{tab:overview}
  \vspace{-7mm}
\end{table*}

@@

\maciek{Figure: cluster signatures}

@@

\maciek{Rewrite: cluster types should be cluster signatures}
In our analysis, we distinguish among three types of clusters: $C_1, C_2, C_3$. In a cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.
Before bounding the competitive ratio of \TAlg, we introduce the lemma that estimates the cost of a single repartition of \TAlg.

@@

\begin{proof}
  \maciek{Danger zone, nothing is finished here}

  A \emph{signature} of a cluster $C$, denoted $S(C)$ is a multiset of sizes of components located in this cluster.
  Note that there are $p(k)$ possible signatures.

  Consider a repartition from a perspective of a single cluster.
  Prior to the repartition, it had a signature $S^-(C)$, and after the repartition it has a signature $S^+(C)$.
\end{proof}
